---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# manders1D


Given two channels (from fluorescence microscopy), use one channel for
    thresholding and define "domains", then evaluate the intensity of the second channel
    within the domains.
    
    
## Installation

You can install the development version of manders1D from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AlexWeinreb/manders1D")
```

## Example step by step

Given a directory (corresponding to a condition, e.g. a genotype), which contains csv files (corresponding to individual biological replicates), all the files in the directory can be read with:

```{r eval=FALSE}
library(manders1D)
genotype_dir <- "data/genotype1/"

data <- read_condition(genotype_dir)
```

```{r echo=FALSE}
library(manders1D)
genotype_dir <- "../melissa/input/csvs/EN9174/"

data <- read_condition(genotype_dir)
```

The resulting file has columns `condition` (the name of the directory), `individual` (the name of the csv file), `values.C1` and `values.C2` (which had to be columns in the csv files).

```{r}
head(data)
```

Each individual can be processed by `threshold_peaks_one_individual()`:

```{r}
first_individual <- unique(data$individual)[[1]]
data_single_ind <- data[ data$individual == first_individual, ]

quantif_single_individual <- threshold_peaks_one_individual(data_single_ind)
head(quantif_single_individual)
```



## Example in single command

Alternatively, the command `process_whole_directory()` runs all these steps given an input an output directory:

```{r eval=FALSE}
library(manders1D)

process_whole_directory(input_dir = "data/input/genotype1",
                        output_dir = "data/output/genotype1")
```



